What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
work on abstract

\newcommand{\XXX}[1]{\textcolor{red}{{\it \textbf{[XXX: #1]}}}}

@@

\begin{abstract}

  Within the field of mining software repositories, many approaches,   such as topic modeling and concept location, rely on the automated   application of machine learning algorithms to corpora.  This kind of   approach typically makes no use of domain-specific knowledge to   improve the results or put them into a context that a developer can   relate to.  While too much specificity can produce non-generalizable   results, too little produces broad learners that do not provide much   immediately useful detail.  In this paper, we investigate what   topics the latent topic extractors produce, and examine whether   such topics can be generalized across software products.  We focus   on non-functional requirements related to software quality as a   potential generalization, since there is some shared belief that   these qualities apply broadly across many software systems and their   development artifacts.  In our approach, we name topics based on a   static ontology of non-functional requirements and software   qualities; in essence, this adds context to general-purpose   ontologies such as WordNet.  In this paper, we discuss how we use   this software development domain knowledge to better annotate topics   of development that are extracted from the change log messages in   configuration management systems such as CVS.  Since our taxonomy is   global in scope, our results allow us to compare the relative   importance of particular qualities across different projects. Within the topics extracted from MySQL and MaxDB we found that   non-functional requirements were common and often were trends across   time. Our automated techniques can label topics without much computational overhead.

@@

With respect to the questions raised in section \ref{sec:suplearn}:
\textbf{Do label frequencies change over time?} -- Yes, MySQL's label
frequencies decreased as it got older. Usability and reliability
labels became more and more infrequent as it matured. Maintainability topics
became more prevalent as MaxDB matured.

\textbf{Do the different projects differ in their relative topic
  interest?} -- Yes. MySQL 3.23 had proportionally more
functionality labelled topics, while MaxDB had proportionally more
efficiency and portability related topics.

@@

% Not sure how do handle this
\end{comment}
The idea of extracting higher-level `concerns' (also known as `concepts', `aspects' or `requirements') has been attacked in two ways.

>>>>

\newcommand{\XXX}[1]{\textcolor{red}{{\it \textbf{[XXX: #1]}}}}
\hyphenation{Max-DB}

@@

\begin{abstract}
  Within the field of mining software repositories, approaches such as topic modeling and concept location rely on the automated   application of machine learning algorithms to corpora.  %What is a 'topic'?

% Other approaches

This kind of approach typically makes no use of domain-specific knowledge to improve the results or put them into a context that a developer can relate to.  While too much specificity can produce non-generalizable results, too little produces broad learners that do not provide much immediately useful detail.

 In this paper, we investigate what topics the latent topic extractors produce, and examine whether such topics can be generalized across software products.  We focus on non-functional requirements related to software quality as a potential generalization, since there is some shared belief that these qualities apply broadly across many software systems and their development artifacts.  In our approach, we name topics based on a static ontology of non-functional requirements and software qualities; in essence, this adds context to general-purpose ontologies such as WordNet.  In this paper, we discuss how we use this software development domain knowledge to better annotate topics of development that are extracted from the change log messages in configuration management systems such as CVS.  Since our taxonomy is global in scope, our results allow us to compare the relative importance of particular qualities across different projects. Within the topics extracted from MySQL and MaxDB we found that non-functional requirements were common and often were trends across time. Our automated techniques can label topics without much computational overhead.

@@

With respect to the questions raised in section \ref{sec:suplearn}:

\textbf{Do label frequencies change over time?} -- Yes, MySQL's label
frequencies decreased as it got older. Usability and reliability
labels became more and more infrequent as it matured. Maintainability topics
became more prevalent as MaxDB matured.
\textbf{Do the different projects differ in their relative topic
  interest?} -- Yes. MySQL 3.23 had proportionally more
functionality labelled topics, while MaxDB had proportionally more
efficiency and portability related topics.

@@

% Not sure how do handle this
\end{comment}
The idea of extracting higher-level `concerns' (also known as `concepts', `aspects' or `requirements') has been approached in two ways.
